---
title: "Making Graphs Worthy of Stack Overflow"
author: "David Robinson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Graphing Stack Overflow Trends with Freehand Circles}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo = FALSE}
library(knitr)
opts_chunk$set(fig.width = 5, fig.height = 5)
set.seed(2015-04-01)
```

The ggfreehand package allows one to add freehand red circles to a plot. This can improve many plots, but most importantly those that are to be posted on the Stack Exchange network.

For example, we'll use the [stackr](https://github.com/dgrtwo/stackr) package to download all the answers from about a Stack Overflow user (me):

```{r, eval = FALSE}
library(stackr)
answers <- stack_users(712603, "answers", num_pages = 10, pagesize = 100)

library(dplyr)
answers <- tbl_df(answers)
```

If you'd rather not use the stackr package, note that the `ggfreehand` package provides this data (as of 4/1/15) as a built-in dataset:

```{r}
library(ggfreehand)
data(answers)
```

Suppose we are interested in number of answers per month, much as I analyze [here](http://meta.stackoverflow.com/a/252757/712603). We could find the number of answers per month like so:

```{r}
library(dplyr)
library(lubridate)
library(ggplot2)

answers_per_month <- answers %>%
    mutate(month = round_date(creation_date, "month")) %>%
    count(month)
```

This lets us use ggplot2 to create a graph of answers per month over time:

```{r}
library(ggplot2)
ggplot(answers_per_month, aes(month, n)) + geom_line()
```

### What this graph is missing: more freehand red circles

User [wooble](http://meta.stackoverflow.com/users/110707/wooble) noted a critical problem with this graph [in this comment](http://meta.stackoverflow.com/questions/252756/are-high-reputation-users-answering-fewer-questions/252757#comment9735_252757):

> -1; needs more freehand red circles on the graphs.

This is indeed a huge problem! As described [here](http://meta.stackexchange.com/a/19775/176330) in the "Many Memes of Meta", the freehand red circle is a long-standing tradition of Meta, one that has been scientifically proven to draw the user's attention more effectively than any other shape [citation needed].

Unfortunately ggplot2 doesn't provide a layer for adding freehand circles, but the `ggfreehand` package does! Let's say we want to circle the two months in which I answered the most questions.

```{r}
top_2 <- answers_per_month %>% top_n(2, n)
top_2
```

We can now add those as freehand circles with the `geom_freehand` layer.

```{r}
ggplot(answers_per_month, aes(month, n)) + geom_line() +
    geom_freehand(data = top_2)
```

This is *much* more worthy of being posted on Meta Stack Overflow. If those circles are too messy or too neat for you, you can turn down or up the `noisiness` parameter:

```{r}
ggplot(answers_per_month, aes(month, n)) + geom_line() +
    geom_freehand(data = top_2, noisiness = 2)

ggplot(answers_per_month, aes(month, n)) + geom_line() +
    geom_freehand(data = top_2, noisiness = 10)
```

You can also make the circle bigger or smaller. (The data is normalized such that a radius of 1 causes the freehand circle to take up 1/25 of the plot's height and width)

```{r}
ggplot(answers_per_month, aes(month, n)) + geom_line() +
    geom_freehand(data = top_2, radius = 3)

ggplot(answers_per_month, aes(month, n)) + geom_line() +
    geom_freehand(data = top_2, radius = .2)
```
